---
title: "Class 8 Exercises"
output: html_document
date: "2024-04-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rethinking)
```

## Exercises

### Easy

Do all the easy exercises from Chapter 9: **9E1** through **9E6**.

#### 9E1. Which of the following is a requirement of the simple Metropolis algorithm?
(1) The parameters must be discrete.
(2) The likelihood function must be Gaussian.
(3) The proposal distribution must be symmetric.

3rd option it issss:
"Provided the way we choose our proposed parameter values at each step is symmetric—so
that there is an equal chance of proposing from A to B and from B to A—then the Metropolis
algorithm will eventually give us a collection of samples from the joint posterior."


#### 9E2. Gibbs sampling is more efficient than the Metropolis algorithm. How does it achieve this extra
efficiency? Are there any limitations to the Gibbs sampling strategy?

- Need fewer samples than in Metropolis Algorithm to get an equally good image of the posterior distribution
- Limitations: Something about conjugate priors. When models become too complex they are both quite inefficient: for an example when two parameters are correlated it enters the problem of 'the two leg example'.


#### 9E3. Which sort of parameters can Hamiltonian Monte Carlo not handle? Can you explain why?

- Cannot handle parameters that are not continuous as it can't glide through discrete parameters. 
- It needs a continuous space to move around in - Many smaller islands won't be good. 


#### 9E4. Explain the difference between the effective number of samples, n_eff as calculated by Stan,
and the actual number of samples.

#### 9E5. Which value should Rhat approach, when a chain is sampling the posterior distribution correctly?

#### 9E6. Sketch a good trace plot for a Markov chain, one that is effectively sampling from the posterior
distribution. What is good about its shape? Then sketch a trace plot for a malfunctioning Markov
chain. What about its shape indicates malfunction?


### Medium

#### 9M1

```{r}

# Your solution here

```

#### 9M2

```{r}

# Your solution herre

```

### Hard

#### 9H1

```{r}

# Your solution here

```

#### 9H2

```{r}

# Your solution herre

```
